\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  % \vspace{-4pt}
  \color{gray}  \item
% Last Updated on January 12th, 2024
\end{flushright}

\vspace{-7pt}

\begin{center}
    \textbf{\Huge \scshape Kathan Kathrotiya} \\ \vspace{5pt}
    \small 
    \faIcon{phone-alt} \ \small 958-656-6717 $  $
    \faIcon{envelope}
    \href{mailto:kathankathrotiya@gmail.com}
    {{kathankathrotiya@gmail.com}} $  $
    \faIcon{github}
    \href{https://github.com/Kathankathrotiya}{{github.com/Kathankathrotiya}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/kathankathroitya/}{{linkedin.com/in/kathankathrotiya}} $  $
    
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Nirma University}{June 2025}      
      {B.Tech Computer Science and Engineering}{Current GPA: 9.09}
      \vspace{1pt}
    \resumeSubheading
      {P.V. Modi High School}{May 2021}
      {JEE Mains (98.54) \& JEE Advanced Qualified}{Board PR: 98.97}

    \vspace{2pt}

  \resumeSubHeadingListEnd


% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
        {\href{https://github.com/Kathankathrotiya/WhatsApp-Chat-Analyzer}{\faIcon{external-link-alt} \textbf{ WhatsApp-Chat-Analyzer}} $|$ \footnotesize\emph{Python, Streamlit, GloVe, CNN, BiLSTM, Plotly, Matplotlib, Pandas}} {Sept. 2023} \\
        \resumeItemListStart
            \resumeItem{Developed an interactive user interface using Streamlit and Python libraries to facilitate user engagement.}
            \resumeItem{Implemented GloVe embeddings for data preprocessing, to efficiently structure raw chat data.}
            \resumeItem{Integrated deep learning model for sentiment analysis, leveraging Convolutional Neural Network (CNN) and Bidirectional Long Short-Term Memory (BiLSTM) layers.}
            \resumeItem{Achieved a commendable 78\% accuracy by strategically employing the Adam optimizer during the training of the sentiment analysis model.}
          \resumeItemListEnd

        \resumeProjectHeading
         {\href{https://github.com/Kathankathrotiya/Hospital-Management-System}{\faIcon{external-link-alt} \textbf{ Hospital-Management-System}} $|$ \footnotesize\emph{Python, Flask, SQLAlchemy, MySQL, Werkzeug, HTML, Jinja}}{Mar. 2023} \\
        \resumeItemListStart
            \resumeItem{Developed a Flask-based web application that serves as a comprehensive Hospital Management System, streamlining processes for doctors, patients, and administrators.}
            \resumeItem{Implemented secure user authentication features with Flask-Login, ensuring a seamless and secure experience for users during registration, login, and logout.}
            \resumeItem{Designed and integrated a relational database using SQLAlchemy, facilitating efficient data management for doctors, patients, and appointments. Implemented CRUD functionalities to enable easy manipulation of records.}
          \resumeItemListEnd
          
        \resumeProjectHeading
         {\href{https://github.com/Kathankathrotiya/Break-the-Bricks}{\faIcon{external-link-alt} \textbf{ Break-the-Bricks}} $|$ \footnotesize\emph{Java, Swing, Graphics2D, IntelliJ}}{Oct. 2022} \\
        \resumeItemListStart
            \resumeItem{Engineered a dynamic 2D breakout-style game in Java, applying OOP principles to implement robust game logic, precise collision detection, and an efficient scoring system.}
            \resumeItem{Designed and developed the GUI using the Swing library, creating responsive UI elements such as paddles and implementing smooth animations for enhanced user experience.}
            \resumeItem{Implemented a modular and scalable code structure, utilizing Graphics2D for rendering and optimizing code for improved readability and performance.}
          \resumeItemListEnd

        \resumeProjectHeading
        {\href{https://github.com/Kathankathrotiya/Movie-Ticket-Booking-System}{\faIcon{external-link-alt} \textbf{ Movie-Ticket-Booking-System}} $|$ \footnotesize\emph{C/C++, Visual Studio Code}}{May. 2022}\\
        \resumeItemListStart
            \resumeItem{Engineered a console-based Movie Ticket Booking System in C, providing users an intuitive interface for selecting movies, choosing seats, and booking them.}
            \resumeItem{Designed a user-friendly application with dynamic ticket generation, offering a straightforward and efficient process for users to book, cancel tickets, and receive detailed booking confirmations—all within the console environment.}
          \resumeItemListEnd
          
          
    \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{

     \textbf{Coursework}{: Data Structures and Algorithms, Object-Oriented Programming, Computer Networks, Database Management System, Machine Learning, Computer Architecture and Cloud Computing (AWS)} \\
     \textbf{Languages}{: C/C++, Python, Java, JavaScript, HTML,CSS} \\
     
     \textbf{Frameworks}{: React, Flask, Angular, WordPress} \\
     
     \textbf{Libraries}{: NumPy, Pandas,Matplotlib,Seaborn,Scikit-learn,TensorFlow,Keras,NLTK}  \\

     \textbf{IDEs}{: PyCharm, Visual Studio Code, Jupyter Notebook, IntelliJ} \\

     
    }}
 \end{itemize}

% -------------------- EXPERIENCE --------------------
\section{Achievements}
  \resumeSubHeadingListStart

          \resumeProjectHeading
         {\textbf{5 Star \& Problem Solving (Intermediate) Certified} $|$ \footnotesize\emph{HackerRank} $   $ {\href{https://www.hackerrank.com/certificates/228e8148a4c5}{\faIcon{external-link-alt}}}\vspace{7pt}}{}
        {\small{Solved Algorithms and Data Structures problems}}

            \resumeProjectHeading
          {\textbf{Master Round Qualified} $|$ \footnotesize\emph{Innovate India Coding Championship} $   $ {\href{https://drive.google.com/file/d/1lgHcKFil0cDZerXFaCmNcrPnoiFC0OWK/view?usp=drive_link}{\faIcon{external-link-alt}}}\vspace{7pt}}{Jul. 2022} \\
          {\small{Cleared Aptitude test and Coding Round}}
    \resumeSubHeadingListEnd 

    

\end{document}
